Distinction Centrality Analysis

### 2025-07-17 analysis.qmd
some new stuff

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source("distinction.R")
```

```{r}
   tab.cent <- function(x, d = 3, name = "name", caption = "", label = "label") { #table function
   library(kableExtra)
   t <- kbl(x, 
            format = "latex", booktabs = TRUE, linesep = "",
            digits = d, row.names = FALSE,
            col.names = c("Node", "Distinction", "SDistinction", "Status", "Constraint", "Scalar"),
            caption = caption, label = label
            ) %>% 
            kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>% 
            save_kable(file = here("Tabs", paste(name, ".tex", sep = "")))
   }
```

@@

```{r}
   plot.graph.norm <- function(x, l = "kk", vs = 12, ts = 6) { #plotting function
      library(ggraph)
      d <- distinction(x)[,3]
      nc <- rep("", length(d))
      nc[which(d < -0.05)] <- "red"
      nc[which(d > 0.05)] <- "blue"
      nc[which(d <= 0.05 & d >= -0.05)] <- "purple"
      if (is.null(V(x)$name) == TRUE) {
         n <- 1:vcount(x)
         tc <- "white"
         s <- vs
         }
      if (is.null(V(x)$name) == FALSE) {
         n <- V(x)$name
         tc <- nc
         vs <- 0
         }
      p <- ggraph(x, layout = l)
      p <- p + geom_edge_link(color = "steelblue", edge_width = 0.5)
      p <- p + geom_node_point(aes(x = x, y = y), size = vs, color = nc) 
      p <- p + geom_node_text(aes(label = n), size = ts, color = tc, fontface = "bold")
      p <- p + theme_graph() 
   return(p)
   }
```

```{r}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1)
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2)
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3)
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4)
   dev.off()
```

```{r}
   medici1 <- as.matrix(read.csv(here("Data", "MediciEdgeList.csv")))
   medici1 <- graph_from_edgelist(medici1, directed = FALSE)
   medici2 <- as.matrix(read.csv(here("Data", "MediciEdgeListMarriageCut.csv")))
   medici2 <- graph_from_edgelist(medici2, directed = FALSE)
   nomedici <- as.matrix(read.csv(here("Data", "NoMediciEdgeList.csv")))
   nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
   png(here("Plots", "medici.png"), height = 600, width = 1000)
      plot.graph.norm(medici1, ts = 5)
   dev.off()
   png(here("Plots", "nomedici.png"), height = 600, width = 1000)
      plot.graph.norm(nomedici, ts = 5)
   dev.off()

@@

```{r}
   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
   g <- graph_from_edgelist(g, directed = FALSE)
   distinction(g)
```

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1)
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2)
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3)
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4)
   dev.off()
```

```{r Medici Distinction Plots}
   medici1 <- as.matrix(read.csv(here("Data", "MediciEdgeList.csv")))
   medici1 <- graph_from_edgelist(medici1, directed = FALSE)
   medici2 <- as.matrix(read.csv(here("Data", "MediciEdgeListMarriageCut.csv")))
   medici2 <- graph_from_edgelist(medici2, directed = FALSE)
   nomedici <- as.matrix(read.csv(here("Data", "NoMediciEdgeList.csv")))
   nomedici <- graph_from_edgelist(nomedici, directed = FALSE)
   png(here("Plots", "medici.png"), height = 600, width = 1000)
      plot.graph.norm(medici1, ts = 5)
   dev.off()
   png(here("Plots", "nomedici.png"), height = 600, width = 1000)
      plot.graph.norm(nomedici, ts = 5)
   dev.off()

@@

```{r Search Model Distinction}
   g <- as.matrix(read.csv(here("Data", "searchmodeltest.csv")))
   g <- graph_from_edgelist(g, directed = FALSE)
   distinction(g)
```

```{r}
   make.broker.graphs <- function(n = 10) {
      g <- make_empty_graph(9, directed = FALSE)
      g <- g + edge(1,2)
      g <- g + edge(1,3)
      g <- g + edge(2,4)
      g <- g + edge(2,5)
      g <- g + edge(2,6)
      g <- g + edge(3,7)
      g <- g + edge(3,8)
      g <- g + edge(3,9)
      el <- vector(mode = "list", length = n)
      el[[1]] <- g
      a <- 10
      b <- 11
      c <- 12
      d <- 13
      for (i in 2:n) {
         g <- add_vertices(g, 4)
         g <- g + edge(1,a)
         g <- g + edge(a,b)
         g <- g + edge(a,c)
         g <- g + edge(a,d)
         el[[i]] <- g
         a <- a + 4
         b <- b + 4
         c <- c + 4
         d <- d + 4
      }
   return(el)
   }
   b <- make.broker.graphs(30)
   c <- lapply(b, distinction)
   d <- sapply(c, function(x) {x[2, 2]})
```

    p <- p + geom_node_point(aes(x = x, y = y), size = 18, color = "tan2")

```{r}
   library(patchwork)
   library(ggplotify)
   library(ggraph)
   gg <- function(x) {
      n <- vcount(x)
      V(x)$name <- 1:n
      w <- ggraph(x, layout = "kk") + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c("blue", rep("tan2", n - 1))) + 
      geom_node_text(aes(label = name), color = "white", size = 3) +
      ylim(-4,4) + xlim(-4,4) 
      return(w)
      }
   p.list <- lapply(b, gg)
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Branches =", i+1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:6)], nrow = 2)
   ggsave(here("Plots", "tree-examples.png"), width = 10, height = 7, units = "in")
```

```{r}
   dat <- data.frame(d = d, n = 1:length(d))
   p <- ggplot(dat, aes(n, d, group = 1)) 
   p <- p + geom_point(size = 3, color = "blue")
   p <- p + geom_line(linewidth = 0.75, color = "blue")
   p <- p + geom_hline(yintercept = 0, color = "red", linetype = 2)
   p <- p + labs(y = "Gatekeeper Distinction", x = "Number of Branches")
   p <- p + ylim(-0.1, 1)
   p <- p + theme_minimal()
   p <- p + theme(axis.text = element_text(size = 12),
                  axis.title = element_text(size = 14, face = "bold"))
   p
